%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------


\documentclass[preprint]{sigplanconf}

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}

\begin{document}

\conferenceinfo{WXYZ '05}{date, City.} 
\copyrightyear{2005} 
\copyrightdata{[to be supplied]} 

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Title Text}
\subtitle{Subtitle Text, if any}

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Name2\and Name3}
           {Affiliation2/3}
           {Email2/3}

\maketitle

\begin{abstract}
This is the text of the abstract.
\end{abstract}

\category{CR-number}{subcategory}{third-level}

\terms
term1, term2

\keywords
keyword1, keyword2

\section{Introduction}

The CFA family of analyses [cite k-CFA, gamma-CFA, mu-CFA, etc.] promise to enhance [wc] program efficiency [cite], security [cite], and correctness [cite].

…

Racket programs are organized into modules.
Interaction between different parts of the program is vetted through the module boundary.
An \texttt{import} declaration imports every definition explicitly \texttt{provide}d within the imported module.

While modules are great for managing program complexity, they limit the comprehensiveness of an analysis in the same way … [that inter-procedural analysis enables optimizations otherwise unattainable].
To combat this, modules are first compiled to a high-level intermediate bytecode form and programs are \textit{demodularized} to remove boundaries.
Finally, a demodularized bytecode program is decompiled to a small set of core forms.
[move the following discussion]
These include lambdas, apply-values, define-values, etc.
The compiler performs certain base optimizations such as constant folding [and …] and tracks certain flow information [example], some of which it discovers too late in the compilation process.
This information is propagated to the decompiler and the resultant core forms are annotated with source information and flow metadata potentially useful to a program optimizer.

\section{Method}

The kernel (not the same as core) language of Racket--the language of the VM--contains over 1000 primitives: arithmetic primitives such as \texttt{+}, \texttt{sqrt}, and \texttt{quotient}; I/O primitives such as \texttt{current-print}, etc. We classify particular subsets of these according to pertinent behaviors.
Included in this is domain checking.
If the analyzer can prove that domain constraints are satisfied in a particular context, the checking can be discarded in all instances of that context.

Are parameters/continuation marks going to require anything special from the analyzer?

\subsubsection{Contract Discharge}
As values conceptually pass through this boundary, dynamic contracts may be attached to assist [wc] blame assignment in specification violations.
Racket's higher-order contracts [cite] allow contracts to be attached to higher-order functions [and dynamically track blame through an arbitrary depth of higher-orderness] but impose a dynamic check at each invocation of the function. 
\appendix
\section{Appendix Title}

This is the text of the appendix, if you need one.

\acks

Acknowledgments, if needed.

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

\end{document}
